How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-13 docs/PhysicsPaper/StokesErosion.tex
working on sec 3

%-----------------------------------------------------------------------------------------------%
\section{Boundary Integral Equation and Cauchy Integral Formulation}
\label{sec:DLP}
%-----------------------------------------------------------------------------------------------%
To accurately and efficiently solve the Stokes
  equations~\eqref{eqn:StokesEq}, we reformulate the system as a
  boundary integral equation (BIE). Applying the same approach as our
  previous work~\citep{qua-moo2018}, we represent the velocity as the
  sum of a double-layer potential and a combination of Stokeslets and
  rotlets~\cite{pow-mir1987}
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) + \sum_{\ell=1}^{M}\left(
    S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
    \quad \xx \in \Omega,
  \label{eqn:velocity}
\end{align}
where 
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
  \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
  \eeta(\yy) \, ds_\yy.
  \label{eqn:velocityDLP}
\end{align}
Note that $\bd\Omega$ includes both the eroding bodies and the outer
boundary. The Stokeslet and the rotlets are
\begin{align}
  S[\lambda_\ell](\xx) = \frac{1}{4\pi} \left(\log \rho_\ell +
  \frac{\rr_\ell \otimes \rr_\ell}{\rho_\ell^2} \right) \llambda_\ell,
  \quad
  R[\xi_\ell](\xx) = \frac{\rr_\ell^\perp}{\rho_\ell^2}\xi_\ell,
\end{align}
where $\rr_\ell = \xx - \cc_\ell$, $\rho_\ell = \|\rr_\ell\|$, and
$\cc_\ell$ is a point inside body $\ell$. If the density function,
Stokeslets, and rotlets satisfy the second-kind boundary integral
equation
\begin{subequations}
  \label{eqn:FredBIE}
  \begin{alignat}{3}
    \UU(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
      \sum_{\ell=1}^{M}\left(S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
      \quad &&\xx \in \Gamma, \\
    \mathbf{0} &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
      \sum_{\ell=1}^{M}\left(S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
      &&\xx \in \gamma_\ell, \: \ell = 1,\ldots,M, \\
    \llambda_\ell &= \int_{\gamma_i} \eeta(\yy) \, ds_\yy, 
      &&\ell = 1,\ldots,M, \\
    \xi_\ell &= \int_{\gamma_i} (\yy - \cc_i)^\perp \cdot 
      \eeta(\yy) \, ds_\yy, &&\ell = 1,\ldots,M,
  \end{alignat}
\end{subequations}
then the representation~\eqref{eqn:velocity}
satisfies~\eqref{eqn:StokesEq}. We solve~\eqref{eqn:FredBIE} by choosing
equispaced collocation points on $\gamma_\ell$ and $\Gamma$, and then
replacing the integrals with quadrature rules. This results in a linear
system with a mesh-independent condition number, and it is solved
iteratively with GMRES.

We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_x$, and use similar
notation for $\yy$, $\nn$, and $\eeta$. We also interpret $\gamma$, the
boundary of the $i^{th}$ grain or the bounding box $\Gamma$, as a Jordan
curve in $\CC$. We introduce the functions
\begin{align}
  \tau_1(y) = \eta(y) \overline{n(y)} \Re(n(y)), \quad 
  \tau_2(y) = \eta(y) \overline{n(y)} \Im(n(y)).
\end{align}
We then define the five Cauchy integrals
\begin{align}
  v_1(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{Re(\eta(y))}{x-y} \,dy, 
  \quad
  v_2(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{Im(\eta(y))}{x-y} \, dy, 
  \quad
  v_3(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{Re(\overline{y}\eta(y))}{x-y} \, dy, \\
  v_4(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_1(y)}{x-y} \, dy,
  \quad
  v_5(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_2(y)}{x-y} \, dy.
\end{align}
Then, the first and second components of the Stokes double-layer
potential are
\begin{align}
  u_1(x) &= -\Re(x)\Re(v_1'(x)) - \Im(x)\Re(v_2'(x)) + 
           \Re(v_3'(x)) + \Re(v_4(x)) \\
  u_2(x) &= +\Re(x)\Im(v_1'(x)) + \Im(x)\Im(v_2'(x)) - 
           \Im(v_3'(x)) + \Re(v_5(x)),
\end{align}
respectively. The vorticity can be shown to satisfy
\begin{align}
  \omega(x) = \Im(v_1'(x)) + \Re(v_2'(x)) + 
     \Re(v_5'(x)) + \Im(v_4'(x)).
\end{align}
We note that the vorticity only requires first derivatives of Cauchy
integrals, but the stress tensor involves second derivatives.

The accuracy of the method is determined by the accuracy of the
quadrature rule applied to equation~\eqref{eqn:FredBIE}. A quadrature
rule for~\eqref{eqn:velocityDLP} that achieves spectral accuracy writes
the Stokes double-layer potential as a collection of Cauchy integrals
\begin{align}
  v(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy.
\end{align}
The boundary data of $v(x)$ satisfies the Sokhotski-Plemelj jump relation
\begin{align}
  v^{-}(x_0) = \lim_{\substack{x \rightarrow x_0 \\ x \in \Omega}} \int_{\gamma}
    \frac{\eta(y)}{x-y}\, dy = -\frac{1}{2}\eta(x_0) - 
    \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy,
    \quad x_0 \in \gamma,
    \label{eqn:SP}
\end{align}
where the last integral is interpreted in the principal value sense.
Once $v^{-}$ is calculated, $v(x)$ and its derivatives can be determined
by its boundary data alone using the Cauchy Integral Theorem
\begin{subequations}
  \label{eqn:cauchy}
  \begin{alignat}{3}
  v(x) &= \frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{v^{-}(y)}{y-x} \,dy, \\
  v'(x) &= \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{v^{-}(y)}{(y-x)^2} \, dy, \\
  v''(x) &= \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{v^{-}(y)}{(y-x)^3} \, dy.
  \end{alignat}
\end{subequations}
Note that we require second-order derivatives to compute the shear
stress.

@@

%-----------------------------------------------------------------------------------------------%
\subsection{Boundary Integral Representation in $\RR^2$}
%-----------------------------------------------------------------------------------------------%

\vsp{2} \nick{Finished rewording up to here} \vsp{2}

Once~\eqref{eqn:BIE} is solved for the density function $\eeta$, the
corresponding deformation tensor, pressure, and vorticity at $\xx \in
\Omega$ are written in terms of layer potentials~\citep{qua-moo2018}.
To compute the deformation tensor for $\xx \in \gamma$, we include the
jump term
\begin{align}
  \frac{1}{2} \left(\pderiv{\eeta}{\ss} \cdot \ss \right) \left[
    \begin{array}{cc}
      s_x^2 - s_y^2 & 2s_x s_y \\ 2s_x s_y & s_y^2 - s_x^2
    \end{array}
  \right].
  \label{eqn:deformationJump}
\end{align}
Finally, the deformation tensor, pressure, and vorticity due to the
Stokeslets and rotlets are readily available~\citep{poz1992}. Having
computed the deformation tensor on $\gamma$, the shear stress is
computed using equation~\eqref{eqn:shearStress}.

%-----------------------------------------------------------------------------------------------%
\subsection{Cauchy Integral Formulation}
\label{sec:DLPcomplex}
%-----------------------------------------------------------------------------------------------%
The velocity double-layer potential~\eqref{eqn:velocityDLP}, and its
corresponding deformation tensor, pressure, and vorticity are all
written as layer potentials in $\RR^2$. However, the quadrature method
we introduce in section~\ref{sec:method} requires complex-valued
representations. The first step to form a complex representation is to
write the Laplace double-layer potential as the complex integral
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2}\eeta(\yy)\, ds_\yy = \Real (v(x)),
\end{align}
where
\begin{align}
  v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x - y} \, dy, \quad x \in \Omega.
  \label{eqn:laplaceComplex}
\end{align}
Here $x = x_1 + i x_2,y = y_1 + i y_2 \in \CC$ are the complex
counterparts of $\xx = (x_1,x_2),\yy = (y_1,y_2) \in \RR^2$, and $\eta =
\eta_1 + i \eta_2$ is the complex counterpart of $\eeta =
(\eta_1,\eta_2)$. Therefore, depending on the formulation of the layer
potential, $\Omega$ is interpreted as a subset of $\RR^2$ or $\CC$.
Equation~\eqref{eqn:laplaceComplex} is converted to a Cauchy integral by
first finding the boundary data of $v$. If $\Omega$ is a
simply-connected interior domain, then the boundary data of $v$
satisfies the Sokhotski-Plemelj jump relation
\begin{align}
  \label{eqn:SPrelation}
  v(x) = - \frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
\end{align}
For exterior domains, the jump term changes from $-1/2$ to $1/2$, and
for multiply-connected domains, such as a porous media, $\bd\Omega$ is
decomposed into its different connected components and the appropriate
jump relation is applied.  Having computed the boundary data of the
holomorphic function $v$, by the Cauchy integral theorem we have
\begin{subequations}
  \label{eqn:cauchy}
  \begin{alignat}{3}
  v(x) &= \frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{v(y)}{y-x} \,dy, \\
  v'(x) &= \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^2} \, dy, \\
  v''(x) &= \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^3} \, dy,
  \end{alignat}
\end{subequations}
for $x \in \Omega$.  Since $v(x)$ depends on the complex-valued density
function $\eta$, we use the notation $v[\eta](x)$ for the holomorphic
function defined in equation~\eqref{eqn:laplaceComplex}, and its first
two derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.

Finally, the Stokes double-layer potential~\eqref{eqn:velocityDLP} can
be written using a Laplace double-layer
potential~\eqref{eqn:laplaceComplex} and its gradients 
\begin{equation}
  \label{eqn:Stokes2Laplace}
  \begin{aligned}
    \DDD[\eeta](\xx) &= 
      \frac{1}{2\pi} \int_{\bd\Omega} 
        \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
      \frac{1}{2\pi} \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
      &- \frac{1}{2\pi} x_1 \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
      \frac{1}{2\pi} x_2 \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
  \end{aligned}
\end{equation}
Therefore, the Stokes double-layer potential can be written as a sum of
Cauchy integrals and its first derivative~\citep{bar-wu-vee2015}
\begin{equation}
  \begin{aligned}
    u_1(x) &= \Real (v[\psi_1](x)) + \Real (v'[y\cdot\eta](x)) 
             -x_1\Real (v'[\eta_1](x)) - x_2\Real (v'[\eta_2](x)), \\
    u_2(x) &= \Real (v[\psi_2](x)) - \Imag (v'[y\cdot\eta](x)) 
         +x_1\Imag (v'[\eta_1](x)) + x_2\Imag (v'[\eta_2](x)),
  \end{aligned}
  \label{eqn:cauchyVelocity}
\end{equation}
where $y \cdot \eta = y_1 \eta_1 + y_2 \eta_2$, 
\begin{align} 
  \psi_1=(\eta_1+i\eta_2)\frac{\Real(n)}{n}, \quad
  \psi_2=(\eta_1+i\eta_2)\frac{\Imag(n)}{n},
\end{align}
and $n \in \CC$ is the complex counterpart of the outward unit normal
$\nn \in \RR^2$.

>>>>

%-----------------------------------------------------------------------------------------------%
\section{Boundary Integral Equation and Cauchy Integral Formulation}
\label{sec:DLP}
%-----------------------------------------------------------------------------------------------%
To accurately and efficiently solve the Stokes
  equations~\eqref{eqn:StokesEq}, we reformulate the system as a
  boundary integral equation (BIE). Applying the same approach as our
  previous works~\citep{quaife2018boundary, chiu2020viscous}, we
  represent the velocity as the sum of a double-layer potential and a
  combination of Stokeslets and rotlets~\cite{pow-mir1987}
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) + \sum_{\ell=1}^{M}\left(
    S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
    \quad \xx \in \Omega,
  \label{eqn:velocity}
\end{align}
where 
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
  \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
  \eeta(\yy) \, ds_\yy.
  \label{eqn:velocityDLP}
\end{align}
Note that $\bd\Omega$ includes both the eroding bodies and the outer
boundary. The Stokeslet and the rotlets are
\begin{align}
  S[\lambda_\ell](\xx) = \frac{1}{4\pi} \left(\log \rho_\ell +
  \frac{\rr_\ell \otimes \rr_\ell}{\rho_\ell^2} \right) \llambda_\ell,
  \quad
  R[\xi_\ell](\xx) = \frac{\rr_\ell^\perp}{\rho_\ell^2}\xi_\ell,
\end{align}
where $\rr_\ell = \xx - \cc_\ell$, $\rho_\ell = \|\rr_\ell\|$, and
$\cc_\ell$ is a point inside body $\ell$. If the density function,
Stokeslets, and rotlets satisfy the second-kind boundary integral
equation
\begin{subequations}
  \label{eqn:FredBIE}
  \begin{alignat}{3}
    \UU(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
      \sum_{\ell=1}^{M}\left(S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
      \quad &&\xx \in \Gamma, \\
    \mathbf{0} &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
      \sum_{\ell=1}^{M}\left(S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
      &&\xx \in \gamma_\ell, \: \ell = 1,\ldots,M, \\
    \llambda_\ell &= \int_{\gamma_\ell} \eeta(\yy) \, ds_\yy, 
      &&\ell = 1,\ldots,M, \\
    \xi_\ell &= \int_{\gamma_\ell} (\yy - \cc_\ell)^\perp \cdot 
      \eeta(\yy) \, ds_\yy, &&\ell = 1,\ldots,M,
  \end{alignat}
\end{subequations}
then the representation~\eqref{eqn:velocity} satisfies the Stokes
equations with the required boundary conditions~\eqref{eqn:StokesEq}. We
solve~\eqref{eqn:FredBIE} by discretizing $\gamma_\ell$ and $\Gamma$ at
equispaced collocation points, and then replacing the integrals with
quadrature rules. This results in a linear system with a
mesh-independent condition number, and it is solved iteratively with
GMRES.

Instead of evaluating the Stokes double-layer
potential~\eqref{eqn:velocityDLP} as a contour integral in $\RR^2$, we
convert the integral to a sum of contour integrals around Jordan curves
in $\CC$. We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_x$, and use
similar notation for $\yy$, $\nn$, and $\eeta$. We also interpret
$\gamma$, the boundary of the $i^{th}$ grain or the bounding box
$\Gamma$, as a Jordan curve in $\CC$. We introduce the functions
\begin{align}
  \tau_1(y) = \eta(y) \overline{n(y)} \Re(n(y)), \quad 
  \tau_2(y) = \eta(y) \overline{n(y)} \Im(n(y)).
\end{align}
We then define the five Cauchy integrals
\begin{align}
  v_1(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{Re(\eta(y))}{x-y} \,dy, 
  \quad
  v_2(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{Im(\eta(y))}{x-y} \, dy, 
  \quad
  v_3(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{Re(\overline{y}\eta(y))}{x-y} \, dy, \\
  v_4(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_1(y)}{x-y} \, dy,
  \quad
  v_5(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_2(y)}{x-y} \, dy.
\end{align}
Then, the first and second components of the Stokes double-layer
potential are
\begin{subequations}
  \begin{align}
    u_1(x) &= -\Re(x)\Re(v_1'(x)) - \Im(x)\Re(v_2'(x)) + 
             \Re(v_3'(x)) + \Re(v_4(x)) \\
    u_2(x) &= +\Re(x)\Im(v_1'(x)) + \Im(x)\Im(v_2'(x)) - 
             \Im(v_3'(x)) + \Re(v_5(x)),
  \end{align}
  \label{eqn:velocityCauchy}
\end{subequations}
respectively. The hydrodynamic components of the deformation tensor are
\begin{subequations}
  \begin{align}
    \pderiv{u_1}{x_1} &= -\Re(v'_1(x)) + \Re(v''_3(x)) + \Re(v'_4(x))
                         -\Re(x)\Re(v''_1(x)) - \Im(x)\Re(v''_2(x)) \\
    \pderiv{u_1}{x_2} &= -\Re(v'_2(x)) - \Im(v''_3(x)) - \Im(v'_4(x))
                         +\Re(x)\Im(v''_1(x)) + \Im(x)\Im(v''_2(x)) \\
    \pderiv{u_2}{x_1} &= +\Im(v'_1(x)) - \Im(v''_3(x)) + \Re(v'_5(x))
                         +\Re(x)\Im(v''_1(x)) + \Im(x)\Im(v''_2(x)) \\
    \pderiv{u_2}{x_2} &= +\Im(v'_2(x)) - \Re(v''_3(x)) - \Im(v'_5(x))
                         +\Re(x)\Re(v''_1(x)) + \Im(x)\Re(v''_2(x)) 
  \end{align}
  \label{eqn:deformationCauchy}
\end{subequations}
Having the deformation tensor at hand, the vorticity can be shown to
satisfy
\begin{align}
  \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
     \Im(v_1'(x)) + \Re(v_2'(x)) + \Re(v_5'(x)) + \Im(v_4'(x)).
  \label{eqn:vorticityCauchy}
\end{align}
We note that the deformation tensor requires second-order derivatives of
Cauchy integrals, but the vorticity only requires first-order
derivatives.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Quadrature for Cauchy integrals}
The accuracy of our method is determined by the accuracy of the
quadrature rule applied to equation~\eqref{eqn:FredBIE}. Since we have
written the Stokes double-layer potential
velocity~\eqref{eqn:velocityCauchy}, deformation
tensor~\eqref{eqn:deformationCauchy}, and
vorticity~\eqref{eqn:vorticityCauchy} as a sum of Cauchy integrals and
their derivatives, the accuracy of the method depends on the accuracy of
computing a general Cauchy integral
\begin{align}
  v(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy.
  \label{eqn:cauchy1}
\end{align}
Here we describe a quadrature formulae that was first used to
approximate analytic functions~\cite{ioa-pap-per1991}, and then extended
to Stokes layer potentials~\cite{bar-wu-vee2015}. The quadrature
requires the boundary data of the analytic function~\eqref{eqn:cauchy1}
which satisfies the Sokhotski-Plemelj jump relation
\begin{align}
  v^{-}(x_0) = \lim_{\substack{x \rightarrow x_0 \\ x \in \Omega}} \int_{\gamma}
    \frac{\eta(y)}{x-y}\, dy = -\frac{1}{2}\eta(x_0) - 
    \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy,
    \quad x_0 \in \gamma,
    \label{eqn:SP}
\end{align}
where the last integral is interpreted in the principal value sense.
Once $v^{-}$ is calculated, $v(x)$ and its derivatives can be determined
by its boundary data alone using the Cauchy Integral Theorem
\begin{subequations}
  \label{eqn:cauchy}
  \begin{alignat}{3}
  \label{eqn:cauchyv}
  v(x) &= \frac{1}{2\pi i}\int_{\gamma} 
    \frac{v^{-}(y)}{y-x} \,dy, \\
  v'(x) &= \frac{1}{2\pi i} \int_{\gamma}
    \frac{v^{-}(y)}{(y-x)^2} \, dy, \\
  v''(x) &= \frac{1}{\pi i} \int_{\gamma}
    \frac{v^{-}(y)}{(y-x)^3} \, dy.
  \end{alignat}
\end{subequations}

To approximate the Cauchy integrals and its
derivatives~\eqref{eqn:cauchy}, the trapezoid rule achieves spectral
accuracy. For example, the Cauchy integral~\eqref{eqn:cauchyv} can be
approximated as
\begin{align}
  v(x) \approx \frac{1}{2\pi i} \sum_{j=1}^{N} 
    w_j \frac{v^{-}(y_j)}{y_j - x},
  \label{eqn:trap}
\end{align}
where $y_j$ are equispaced points on $\gamma$, $w_j = L/N$, and $L$ is
the length of $\gamma$. Because the integrand is both periodic and
smooth, given a fixed points $x$, the trapezoid rule achieves spectral
accuracy~\cite{tre-wei2014}. However, for a fixed $N$, the quadrature
error is not bounded uniformly with respect to $x$ because the
derivative of the integrand grows without bound as $x$ approaches
$\gamma$. This error is problematic for many of our simulations since we
allow for eroding bodies to be arbitrarily close to one another. In
contrast to the Cauchy integral~\eqref{eqn:cauchyv}, the integrand in
the identity
\begin{align}
  \frac{1}{2\pi i}\int_{\gamma} 
    \frac{v^{-}(y) - v(x)}{y-x} \, dy = 0, \quad x \in \Omega,
  \label{eqn:trap2}
\end{align}
is bounded with respect to $x$, and therefore the error of the trapezoid
rule is bounded with respect to $x$. Applying the trapezoid rule, we
have
\begin{align}
  \frac{1}{2\pi i}\sum_{j=1}^{N} w_{j} 
    \frac{v^{-}(y_j) - v(x)}{y_j - x} \approx 0,
\end{align}
where the error is independent of $x$. Rearranging, we have
\begin{align}
  v(x) \approx \left(\frac{1}{2\pi i}\sum_{j=1}^N 
    \frac{v^{-}(y_j)}{y_j - x} w_j \right) \Bigg/
  \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j - x} w_j \right), 
  \quad x \in \Omega.
  \label{eqn:vBary}
\end{align}
Note that the numerator in~\eqref{eqn:vBary} is identical to
equation~\eqref{eqn:trap}, while the denominator is an approximation of
the analytic function $v(x) = 1$. As $x$ approaches $\gamma$, the error
in the numerator and denominator grow, however, since the integrand in
equation~\eqref{eqn:trap2} is bounded independent of $x$, the error of
the ratio is bounded independent of $x$.

@@

%-----------------------------------------------------------------------------------------------%
%\subsection{Boundary Integral Representation in $\RR^2$}
%-----------------------------------------------------------------------------------------------%

%\vsp{2} \nick{Finished rewording up to here} \vsp{2}
%
%Once~\eqref{eqn:BIE} is solved for the density function $\eeta$, the
%corresponding deformation tensor, pressure, and vorticity at $\xx \in
%\Omega$ are written in terms of layer potentials~\citep{qua-moo2018}.
%To compute the deformation tensor for $\xx \in \gamma$, we include the
%jump term
%\begin{align}
%  \frac{1}{2} \left(\pderiv{\eeta}{\ss} \cdot \ss \right) \left[
%    \begin{array}{cc}
%      s_x^2 - s_y^2 & 2s_x s_y \\ 2s_x s_y & s_y^2 - s_x^2
%    \end{array}
%  \right].
%  \label{eqn:deformationJump}
%\end{align}
%Finally, the deformation tensor, pressure, and vorticity due to the
%Stokeslets and rotlets are readily available~\citep{poz1992}. Having
%computed the deformation tensor on $\gamma$, the shear stress is
%computed using equation~\eqref{eqn:shearStress}.

%%-----------------------------------------------------------------------------------------------%
%\subsection{Cauchy Integral Formulation}
%\label{sec:DLPcomplex}
%%-----------------------------------------------------------------------------------------------%
%The velocity double-layer potential~\eqref{eqn:velocityDLP}, and its
%corresponding deformation tensor, pressure, and vorticity are all
%written as layer potentials in $\RR^2$. However, the quadrature method
%we introduce in section~\ref{sec:method} requires complex-valued
%representations. The first step to form a complex representation is to
%write the Laplace double-layer potential as the complex integral
%\begin{align}
%  \DD[\eeta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega} 
%    \frac{\rr \cdot \nn}{\rho^2}\eeta(\yy)\, ds_\yy = \Real (v(x)),
%\end{align}
%where
%\begin{align}
%  v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
%    \frac{\eta(y)}{x - y} \, dy, \quad x \in \Omega.
%  \label{eqn:laplaceComplex}
%\end{align}
%Here $x = x_1 + i x_2,y = y_1 + i y_2 \in \CC$ are the complex
%counterparts of $\xx = (x_1,x_2),\yy = (y_1,y_2) \in \RR^2$, and $\eta =
%\eta_1 + i \eta_2$ is the complex counterpart of $\eeta =
%(\eta_1,\eta_2)$. Therefore, depending on the formulation of the layer
%potential, $\Omega$ is interpreted as a subset of $\RR^2$ or $\CC$.
%Equation~\eqref{eqn:laplaceComplex} is converted to a Cauchy integral by
%first finding the boundary data of $v$. If $\Omega$ is a
%simply-connected interior domain, then the boundary data of $v$
%satisfies the Sokhotski-Plemelj jump relation
%\begin{align}
%  \label{eqn:SPrelation}
%  v(x) = - \frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
%    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
%\end{align}
%For exterior domains, the jump term changes from $-1/2$ to $1/2$, and
%for multiply-connected domains, such as a porous media, $\bd\Omega$ is
%decomposed into its different connected components and the appropriate
%jump relation is applied.  Having computed the boundary data of the
%holomorphic function $v$, by the Cauchy integral theorem we have
%\begin{subequations}
%  \label{eqn:cauchy}
%  \begin{alignat}{3}
%  v(x) &= \frac{1}{2\pi i}\int_{\bd\Omega} 
%    \frac{v(y)}{y-x} \,dy, \\
%  v'(x) &= \frac{1}{2\pi i} \int_{\bd\Omega}
%    \frac{v(y)}{(y-x)^2} \, dy, \\
%  v''(x) &= \frac{1}{\pi i} \int_{\bd\Omega}
%    \frac{v(y)}{(y-x)^3} \, dy,
%  \end{alignat}
%\end{subequations}
%for $x \in \Omega$.  Since $v(x)$ depends on the complex-valued density
%function $\eta$, we use the notation $v[\eta](x)$ for the holomorphic
%function defined in equation~\eqref{eqn:laplaceComplex}, and its first
%two derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.  
%  
%Finally, the Stokes double-layer potential~\eqref{eqn:velocityDLP} can
%be written using a Laplace double-layer
%potential~\eqref{eqn:laplaceComplex} and its gradients 
%\begin{equation}
%  \label{eqn:Stokes2Laplace}
%  \begin{aligned}
%    \DDD[\eeta](\xx) &= 
%      \frac{1}{2\pi} \int_{\bd\Omega} 
%        \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
%      \frac{1}{2\pi} \nabla \int_{\bd\Omega}
%        \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
%      &- \frac{1}{2\pi} x_1 \nabla \int_{\bd\Omega}
%        \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
%      \frac{1}{2\pi} x_2 \nabla \int_{\bd\Omega}
%        \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
%  \end{aligned}
%\end{equation}
%Therefore, the Stokes double-layer potential can be written as a sum of
%Cauchy integrals and its first derivative~\citep{bar-wu-vee2015}
%\begin{equation}
%  \begin{aligned}
%    u_1(x) &= \Real (v[\psi_1](x)) + \Real (v'[y\cdot\eta](x)) 
%             -x_1\Real (v'[\eta_1](x)) - x_2\Real (v'[\eta_2](x)), \\
%    u_2(x) &= \Real (v[\psi_2](x)) - \Imag (v'[y\cdot\eta](x)) 
%         +x_1\Imag (v'[\eta_1](x)) + x_2\Imag (v'[\eta_2](x)),
%  \end{aligned}
%  \label{eqn:cauchyVelocity}
%\end{equation}
%where $y \cdot \eta = y_1 \eta_1 + y_2 \eta_2$, 
%\begin{align} 
%  \psi_1=(\eta_1+i\eta_2)\frac{\Real(n)}{n}, \quad
%  \psi_2=(\eta_1+i\eta_2)\frac{\Imag(n)}{n},
%\end{align}
%and $n \in \CC$ is the complex counterpart of the outward unit normal
%$\nn \in \RR^2$.
%
%%-----------------------------------------------------------------------------------------------%
%\subsection{Cauchy Integral Representation for the Gradient of the
%Double-Layer Potential}
%\label{sec:gradDLPcomplex}
%%-----------------------------------------------------------------------------------------------%
%Computing the shear stress and vorticity requires a complex-valued layer
%potential representation of the velocity gradient.  The deformation
%tensor at $x \in \Omega$ is found by computing the derivatives of the
%expressions for $u_1$ and $u_2$ in equation~\eqref{eqn:cauchyVelocity}  
%\begin{equation}
%\label{eqn:cauchyGradient}
%  \begin{aligned}
%    \pderiv{u_1}{x_1} &= +\Real (v'[\psi_1](x)) + 
%    \Real (v''[y\cdot\eta](x)) - \Real (v'[\eta_1](x)) \\
%    &- x_1\Real (v''[\eta_1](x)) - x_2\Real (v''[\eta_2](x)), \\
%    \pderiv{u_1}{x_2} &= - \Imag (v'[\psi_1](x)) - 
%    \Imag (v''[y\cdot\eta](x)) + x_1\Imag (v''[\eta_1](x)) \\
%    &- \Real (v'[\eta_2](x)) + x_2\Imag (v''[\eta_2](x)), \\
%    \pderiv{u_2}{x_1} &= +\Real (v'[\psi_2](x)) - 
%    \Imag (v''[y\cdot\eta](x)) + \Imag (v'[\eta_1](x))  \\
%    &+ x_1\Imag (v''[\eta_1](x)) + x_2\Imag (v''[\eta_2](x)), \\
%    \pderiv{u_2}{x_2} &= -\Imag (v'[\psi_2](x)) - 
%    \Real (v''[y\cdot\eta](x)) + x_1\Real (v''[\eta_1](x)) \\
%    &+ \Imag (v'[\eta_2](x)) + x_2\Real (v''[\eta_2](x)).
%  \end{aligned}
%\end{equation}
%The same expressions are used to compute the deformation tensor for $x
%\in \bd\Omega$, except that the jump
%condition~\eqref{eqn:deformationJump} is included.  Finally, to compute
%the shear stress, the deformation tensor on $\bd\Omega$ is applied to
%the normal and tangent vectors as in equation~\eqref{eqn:shearStress}.
%The velocity gradient is also used to compute the vorticity in the fluid
%bulk.  For $x \in \Omega$, the Cauchy integral representation of the
%vorticity at $x \in \Omega$ is
%\begin{align}
%  \omega(x) = 
%    \Real (v'[\psi_2](x)) + \Imag (v'[\psi_1](x))+ 
%    \Real (v'[\eta_2](x))+ \Imag (v'[\eta_1](x)).
%\end{align}
%\end{comment}
